Cover letter for the original IJRR submission

### 2017-12-12 body/appendix_algo.tex
algo 1

First, we define an abstract structure State,
that describes a contact configuration.
The use of queues allows a FIFO approach regarding the order 
in which contacts are tested: we try to replace older contacts first when necessary.
Thus the algorithm is deterministic even though it can handle acyclic motions. \\

\begin{lstlisting}]
Struct Limb
{
    // Limb Configuration
    Configuration qk;
    // Effector position in
    // world coordinates
    vector6 pk;
};

Struct State
{
    // root location
    Configuration q0;
    // List of limbs not in contact
    queue<Limb> freeLimbs;
    // List of limbs in contact
    queue<Limb> contactLimbs;
};
\end{lstlisting}

@@

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $list<$State$>$ $states = [s0]$
		\State $nb\_fail = 0$ 
		\State $i = 1;$ /*Current index in the list*/
		\While {$i < length(\mathbf{Q}^0)$}
			\State State $pState = last\_element(states)$
			\State State $s =$ \textsc{GenFullBody}$(pState, \mathbf{Q}^0[i])$
			\If {$s != NULL $}
				\State $nb\_fail = 0$
				\State $i += 1$
				\State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail += 1$
				\If {$nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf				
				\State $s = $\textsc{IntermediateContactState}$(pState)$
			\EndIf
			\State $push\_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
Otherwise, the method \textsc{IntermediateContactState} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.
Algorithm~\ref{alg:pi} gives the pseudo code for \textsc{GenFullBody}.

>>>>

%~ First, we define an abstract structure State,
%~ that describes a contact configuration.
%~ The use of queues allows a FIFO approach regarding the order 
%~ in which contacts are tested: we try to replace older contacts first when necessary.
%~ Thus the algorithm is deterministic even though it can handle acyclic motions. \\
%~ 
%~ \begin{lstlisting}]
%~ Struct Limb
%~ {
    %~ // Limb Configuration
    %~ Configuration qk;
    %~ // Effector position in
    %~ // world coordinates
    %~ vector6 pk;
%~ };
%~ 
%~ Struct State
%~ {
    %~ // root location
    %~ Configuration q0;
    %~ // List of limbs not in contact
    %~ queue<Limb> freeLimbs;
    %~ // List of limbs in contact
    %~ queue<Limb> contactLimbs;
%~ };
%~ \end{lstlisting}

@@

\begin{algorithm}[!tbp]
\caption{Discretization of a path} \label{interpolate}
	\begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
	\Function{Interpolate}{$s0$,$\mathbf{Q}^0$, $MAX\_TRIES$}
		\State $states \gets (s0)$ \Comment{List of states intialized with $s0$}
		\State $nb\_fail \gets 0$ 
		\State $i \gets 1;$ \Comment{Current index in the list}
		\While {$i < length(\mathbf{Q}^0)$}
			\State $pState \gets last\_element(states)$
			\State $s \gets$ \textsc{GenFullBody}$(pState, element(\mathbf{Q}^0,i))$
			\If {$s \not= 0 $}
				\State $nb\_fail \gets 0$
				\State $i \gets i+1$
				\State \textbf{return} $\mathbf{q}^{0}$
			\Else
				\State $nb\_fail \gets nb\_fail + 1$
				\If {$nb\_fail == MAX\_TRIES$}
					\State \textbf{return} $FAILURE$
				\EndIf				
				\State $s \gets $\textsc{IntermediateContactState}$(pState)$
			\EndIf
			\State $push_back(states, s)$
		\EndWhile
		\State \textbf{return} $states$
	\EndFunction
\end{algorithmic}
\label{alg:interpolate}
\end{algorithm}

At each step, \textsc{GenFullBody} is called with the previous state as a parameter, as well
as a new root configuration. \textsc{GenFullBody} returns a new contact configuration, if it succeeded
in computing a configuration with only one contact switch occurring.
Otherwise, the method \textsc{IntermediateContactState} is called.
It repositions one end effector (either a free limb, or the oldest active contact) towards a new contact position if possible.
This repositioning allows to increase the odds that the contact can be maintained at the next step.
The method \textit{last\_element} returns the last element
of the list, \textit{element} returns the element contained by a list at a given index, and \textit{push\_back} inserts an element at the end of a list.
Algorithm~\ref{alg:pi} gives the pseudo code for \textsc{GenFullBody}.
